\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-09 Final Paper/PaperJLin.tex
Added Coef Plots for the Issue Stances Analysis

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Mexico}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Peru}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central/Latin America} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central/Latin America} }
	\label{America}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Germany}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/France}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Western Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Western Europa} }
	\label{WestEuro}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Austria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
	\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Czech}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Poland}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Slovakia}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central Europe} }
	\label{CentEuro}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Finland}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Iceland}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Sweden}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Scandinavia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Scandinavia} }
	\label{Scandinavia}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Bulgaria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Greece}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Montenegro}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Romania}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Southwestern Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Southwestern Europe} }
	\label{SWEuro}
\end{figure}

@@

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/Latvia}}
	\caption[ \tb{Self-Placement Ideology - Eastern Europe} ]
{\tb {Coefficient Plots for Self-Placement Ideology in Eastern Europe} }
\label{EastEuro}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Israel}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Turkey}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Middle East} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Middle East} }
	\label{MidEast}
\end{figure}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Africa}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-1.0519** \\
			&(.4499)\\
			Constant&8.7909*** \\
			& (1.5955) \\
			N& 220\\
			$R^2$&.0660 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table11}
	\end{table}
\end{singlespace}

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/SouthAfrica}}
	\caption[ \tb{Self-Placement Ideology - Africa} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Africa} }
	\label{Africa}
\end{figure}

Africa was originally represented by both Kenya and South Africa. However, with the introduction of controls, the lack of response in one of the areas led to the isolation of South Africa as the sole state in Africa for this analysis. The continent of Africa is one of the most recent places to transition to democracy in the wake of the decolonization movements. However, despite being a democracy for only 20 years, South Africa shows that there are differences between their urban and rural residents with their urban residents rating themselves a full point to the left. It is important to note that place of residence was not directly asked of the participants during the data collection. It is a code used by the researchers for identification purposes. Nonetheless, the results in Table \ref{table11} suggest that there is a significant difference between residents in rural and urban places in a recently transitioned regime in Afrtica, a trend that is not seen in their Central and Eastern European counterparts that share a regime age and level of democracy.

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Japan}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/SouthKorea}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Asia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Asia} }
	\label{Asia}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/NewZealand}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Philippines}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Pacific Islands} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Pacific Island} }
	\label{Pacific}
\end{figure}

@@

In the next section, I turn to the influence of place using an objective measure of beliefs in political actions based on social and economic pollicy and spending. From here, we can see if there is a relationship between how individuals describe themselves and how their objective issue stances play out based on where they live.

@@

Now, we proceed to break down this general analysis by the same regions used to test the \e{Sekf-Identified Ideology} Hypothesis.

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town& .0236 & -.0362   \\
			&(.1004)  & (.0648)\\
			Suburban&-.1950&-.1163 \\
			&(.1549) &  (.0926) \\
			Urban & .1514&.0188 \\
			&(.1195) &(.0846) \\
			Constant&2.920*** &2.001*** \\
			&(.3134) &(.2402) \\
			N&418& 1,159\\
			$R^2$&0.0873 & 0.0512 \\
			\hline 
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{WELib}
\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			Small Town& -.0501 &.1522 & -.1209 \\
			&(.1997) & (.1830) & (.1828) \\
			Suburban&-.0150&.2700  &-.1410  \\
			&(.1651) &(.1852) & (.1745) \\
			Urban &.0677 &.1158  & -.0144 \\
			&(.2131) & (.1819) & (.1578) \\
			Constant&3.9752*** &3.995***  & 3.6204*** \\
			&(.5452) &(.3722) & (.4453) \\
			N&198&372 &284  \\
			$R^2$&0.1154&.1055  & 0.0362 \\  
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{ScanLib}
\end{table}
\end{singlespace}

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}
			\\
			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town& -.0295&-.3396 & & & &  \\
			&(.1228) &(.2166)  &  &  &  &   \\
			Suburban& .3420***&-.4875** &  &  &  &  \\
			&(.1111)& (.2118)  &  &  &  & \\
			Urban&.2230& -.4093** &  &  &  &  \\
			&(.1663)& (.1729) &   &   &  &   \\
			Constant&3.0603***&2.360***  &  &  &  &  \\
			&(.3741)& (.5231)  &  &  &  &  \\
			N&391 & 329  &   &  &   &  \\
			$R^2$&0.0899& 0.1420  &  &  &  &  \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{SWELib}
\end{table}
\end{landscape}

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Mexico}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Peru}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central/Latin America} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central/Latin America} }
	\label{AmericaIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Germany}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/France}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Western Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Western Europa} }
	\label{WestEuroIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Austria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
	\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Czech}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Poland}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Slovakia}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central Europe} }
	\label{CentEuroIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Finland}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Iceland}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Sweden}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Scandinavia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Scandinavia} }
	\label{ScandinaviaIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Bulgaria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Greece}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Montenegro}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Romania}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Southwestern Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Southwestern Europe} }
	\label{SWEuroIdeo}
\end{figure}

@@

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/Latvia}}
	\caption[ \tb{Self-Placement Ideology - Eastern Europe} ]
{\tb {Coefficient Plots for Self-Placement Ideology in Eastern Europe} }
\label{EastEuroIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Israel}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Turkey}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Middle East} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Middle East} }
	\label{MidEastIdeo}
\end{figure}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Africa}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-1.0519** \\
			&(.4499)\\
			Constant&8.7909*** \\
			& (1.5955) \\
			N& 220\\
			$R^2$&0.0660 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table11}
	\end{table}
\end{singlespace}

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/SouthAfrica}}
	\caption[ \tb{Self-Placement Ideology - Africa} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Africa} }
	\label{AfricaIdeo}
\end{figure}

Africa was originally represented by both Kenya and South Africa. However, with the introduction of controls, the lack of response in one of the areas led to the isolation of South Africa as the sole state in Africa for this analysis. The continent of Africa is one of the most recent places to transition to democracy in the wake of the decolonization movements. However, despite being a democracy for only 20 years, South Africa shows that there are differences between their urban and rural residents with their urban residents rating themselves a full point to the left. It is important to note that place of residence was not directly asked of the participants during the data collection. It is a code used by the researchers for identification purposes. Nonetheless, the results in Table \ref{table11} suggest that there is a significant difference between residents in rural and urban places in a recently transitioned regime in Africa, a trend that is not seen in their Central and Eastern European counterparts that share a regime age and level of democracy.

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Japan}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/SouthKorea}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Asia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Asia} }
	\label{AsiaIdeo}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/NewZealand}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Philippines}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Pacific Islands} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Pacific Island} }
	\label{PacificIdeo}
\end{figure}

@@

In the next section, I turn to the influence of place using an objective measure of beliefs in political actions based on social and economic policy and spending. From here, we can see if there is a relationship between how individuals describe themselves and how their objective issue stances play out based on where they live.

@@

Now, we proceed to break down this general analysis by the same regions used to test the \e{Self-Identified Ideology} Hypothesis.

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Mexico}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Peru}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Central/Latin America} ]
	{\tb {Coefficient Plots for Issue Stances in Central/Latin America} }
	\label{AmericaLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town& .0236 & -.0362   \\
			&(.1004)  & (.0648)\\
			Suburban&-.1950&-.1163 \\
			&(.1549) &  (.0926) \\
			Urban & .1514&.0188 \\
			&(.1195) &(.0846) \\
			Constant&2.920*** &2.001*** \\
			&(.3134) &(.2402) \\
			N&418& 1,159\\
			$R^2$&0.0873 & 0.0512 \\
			\hline 
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{WELib}
\end{table}
\end{singlespace}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Germany}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/France}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Western Europe} ]
	{\tb {Coefficient Plots for Issue Stances in Western Europa} }
	\label{WestEuroLib}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Austria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Czech}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Poland}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Central Europe} ]
	{\tb {Coefficient Plots for Issue Stances in Central Europe} }
	\label{CentEuroLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town& -.0501 &.1522 & -.1209 \\
			&(.1997) & (.1830) & (.1828) \\
			Suburban&-.0150&.2700  &-.1410  \\
			&(.1651) &(.1852) & (.1745) \\
			Urban &.0677 &.1158  & -.0144 \\
			&(.2131) & (.1819) & (.1578) \\
			Constant&3.9752*** &3.995***  & 3.6204*** \\
			&(.5452) &(.3722) & (.4453) \\
			N&198&372 &284  \\
			$R^2$&0.1154&.1055  & 0.0362 \\  
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{ScanLib}
\end{table}
\end{singlespace}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Finland}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Iceland}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Sweden}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Scandinavia} ]
	{\tb {Coefficient Plots for Issue Stances in Scandinavia} }
	\label{ScandinaviaLib}
\end{figure}

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}
			\\
			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town& -.0295&-.3396 &-.3025 &.6388*** & -.0862 &.1283  \\
			&(.1228) &(.2166)  &(.2420)  & (.2069) & (.0838)  & (.1352)  \\
			Suburban& .3420***&-.4875** &-.3352  & .6956** & -.2285  & .0263 \\
			&(.1111)& (.2118)  &(.2598)  &(.3059)  & (.2096) & (.1698) \\
			Urban&.2230& -.4093** & -.3739*  & .6014* & .1614* &-.1373  \\
			&(.1663)& (.1729) &(.2263)   & (.3558)  & (.0839) & (.1817)  \\
			Constant&3.0603***&2.360***  & 2.598*** & 3.4274*** &2.6031***  & 3.4728***  \\
			&(.3741)& (.5231)  &(.4582)  &(.8088)  & (.2963) & (.5290)  \\
			N&391 & 329  &458   & 184 & 659  &263  \\
			$R^2$&0.0899& 0.1420  &0.0457  & 0.1014 & 0.0365 & 0.0414 \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{SWELib}
\end{table}
\end{landscape}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Bulgaria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Greece}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Montenegro}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Romania}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Southwestern Europe} ]
	{\tb {Coefficient Plots for Issue Stances in Southwestern Europe} }
	\label{SWEuro}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Eastern Europe}}
		\begin{tabulary}{\linewidth}{l c }
			\\
			\hline
			\tb{Place of Residence} & \tb{Latvia (2014)}  \\
			\hline
			Small Town& -.4632*** \\
			&(.1475)\\
			Suburban&-.2366\\
			&(.2049)\\
			Urban&-.0163\\
			&(.1355)\\
			Constant&2.5914***\\
			&(.3932)\\
			N&276\\
			$R^2$&0.1014\\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{EastELib}
\end{table}
\end{singlespace}

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{LibCoef/Latvia}}
	\caption[ \tb{Issue Stances - Eastern Europe} ]
	{\tb {Coefficient Plots for Issue Stances in Eastern Europe} }
	\label{EastEuroLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.1159&-.1208 \\
			&(.1147)&(.2029) \\
			Suburban&.0637 &.2178 \\
			&(.1312) &(.2178) \\
			Urban&- &.1028 \\
			&- &(.1783)\\
			Constant&3.4492***&1.886*** \\
			&(.3445)&(.5757) \\
			N&379&252 \\
			$R^2$&0.0544&0.0875 \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{MELib}
\end{table}
\end{singlespace}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Israel}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Turkey}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Middle East} ]
	{\tb {Coefficient Plots for Issue Stances in Middle East} }
	\label{MidEastLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Africa}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-.1861 \\
			&(.1871)\\
			Constant&1.989*** \\
			& (.6058) \\
			N& 220\\
			$R^2$&0.0544 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{AfricaLib}
	\end{table}
\end{singlespace}

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{LibCoef/SAfrica}}
	\caption[ \tb{Issue Stances - Africa} ]
	{\tb {Coefficient Plots for Issue Stances in Africa} }
	\label{AfricaLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering 
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Asia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}&\tb{Thailand}\\
			\hline
			Small Town&.2140*&.2990* &-.0567 \\
			&(.1246)&(.1787)  & (.2647) \\
			Suburban&.2256* &.2952 &-.3755 \\
			&(.1307)&(.2937)  & (.4216) \\
			Urban&.1879&.2611  & .8547**\\
			&(.1209)& (.1602) & (.4216) \\
			Constant&3.1767***&2.0334***  & 3.6734*** \\
			&(.3418)& (.5822)  & (.6880) \\
			N&558&328  & 116  \\
			$R^2$&0.0337& 0.0494 & 0.1305 \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{AsiaLib}
\end{table}
\end{singlespace}

%Fix Thailand Figure and Add to graphic later
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/Japan}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/SKorea}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Asia} ]
	{\tb {Coefficient Plots for Issue Stances in Asia} }
	\label{AsiaLibCoef}
\end{figure}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town&-.2018*&-.5318* \\
			&(.1169)&(.3038) \\
			Suburban&- &-.3377 \\
			&-&(.5366) \\
			Urban&-.0508&-.5314*** \\
			&(.1141)& (.1808)\\
			Constant& 4.4689&4.4887*** \\
			&(.3239)& (.7104) \\
			N&565&112 \\
			$R^2$&0.0332& 0.2003 \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{PacificLib}
\end{table}
\end{singlespace}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{LibCoef/NZealand}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{LibCoef/Philippines}
	\end{subfigure}
	\caption[ \tb{Issue Stances - Pacific Islands} ]
	{\tb {Coefficient Plots for Issue Stances in Pacific Island} }
	\label{PacificLibCoef}
\end{figure}
